\section{Previous Employment}

\cventry{2015 -- 2016}{University Health Network}{\textsc{Programmer}}{}{}{Developed mobile apps for android and OS, as well as various web applications. These included creating a medical adherance app in which patient adherenace were tracked and automatic reports were sent to doctors.\\}

\cventry{2011 -- 2012}{Real Programing 4 Kids}{\textsc{Instructor}}{}{}{Taught children ages 7-15 about the fundamentals and good programming practices of computer programming using C++, C\#, Java and Visual Basics. Helped them develop computer games based on the knowledge gained in the course. Communicated effectively by using simple and clear terminology to explain complex terms.\\}

\cventry{2011 -- 2012}{Colours Without Borders}{\textsc{Research Assistant}}{}{}{Used C to acquire data from a device called the i1 pro to acquire colour information of a given colour bar. Analyzed raw spectrum of colour bar and successfully classified individual colours within a colour bar. Used C++ to create a graphical user interface(GUI) for pressman operators to maintain standard consistent colours within a printing job based on expected colour bar information and acquired colour bar information. The GUI communicated to a local and web server via SQL lite, to monitor the progression of a printing job.\\}

\cventry{2010 -- 2012}{Ryerson Signal Analysis Research Groups}{\textsc{Research Assistant}}{}{}{Used MATLAB to analyze spectrum and power densities of various EEG signals. Researched and developed algorithms to efficiently perform analysis. Used intelligent system classification techniques to group similar EEG signals. Developed a GUI in C\# and MATLAB to perform different algorithms on EEG signals. Presented work and findings in weekly conference
meetings.\\}

