\section{Projects}

\cventry{Aug 2015 --
Dec 2015}{CNC Pancake Printing Machine}{\textsc{Mechatronics Design}}{}{}{Wrote LabVIEW code to aquire images of people's faces from a USB camera and perform image processing.  Used MATLAB to convert the processed image to g-code. An Arduino Uno was acting as a CNC controller.  Pancake batter was printed on an electric griddle and color shading was achieved by varying the cooking time.}


\cventry{Aug 2015 --
Dec 2015}{IC Engine Performance Analysis}{\textsc{Mechanical Engineering Laboratory}}{}{}{Determined the change in performance of a turbo-charged 4-cylinder engine as a result of lowering the fuel temperature prior to injection into the cylinders.  Thermocouple and exhaust data was collected using LabVIEW and a dynamometer was used to collect power and torque output readings.}

\cventry{Jan 2015 --
May 2015}{Autonomous Quadrotor}{\textsc{Design of Microprocessor-Based Mechanical Systems}}{}{}{Interfaced a quadrotor with a National Instruments MyRIO, a video camerao, and ultra-sonic sensors.  Wrote a LabVIEW VI that did image processing and controlled the movement of the quadrotor using a PID controller.  The quadrotor was able to track a colored target and follow it.}

\cventry{Aug 2013 --
Dec 2013}{Fishing Simulation}{\textsc{MATLAB Programming}}{}{}{Wrote MATLAB code to create a basic fishing game using a 3-D matrix and a graphical user interface.  Created an algorithm to set fish population, the probability of successfully catching a fish, and to control fish movement within the river.}